Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2019-03-18 Manuscript/manuscript.tex
Small updates

Here, we apply the ECC to the Amber based lipid17 parameters \cite{lipid17-future} of POPS lipid with a monovalent negative charge.
Because POPS carries a physical total charge as ions in water, we apply the theoretically derived scaling factor for
ions $f_q = 0.75$ \cite{leontyev09} to the partial charges of POPS. The lipids with a total charge of -0.75 also neutralize
the counterion charges of +0.75 in simulations with ECC-ions \cite{kohagen16}.
Following our previous work for POPC, we use the scaling factor of $f_\sigma = 0.89$ for the Lennard-Jones~$\sigma$ parameters and
scale the parameters of atoms only in the headgroup, glycerol backbone, and carbonyl regions \cite{melcr18}.
Furhter optimization of parameters was not done in this work.
% we used exactly the pre-determined scaling factor 
%to represent the effects of electronic polarization
%yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}
%polar parts of the phospholipid,
%i.e., charges on all atoms except on alkyl tails, 
%which do not encounter direct contacts with ions.

@@

In the reference simulations with the standard Amber force field,
the Lipid14 parameters~\cite{dickson14} for POPC, the Lipid17 parameters for POPS \cite{lipid17-future},
the TIP3P water model~\cite{jorgensen83}, and ion models by Dang and coworkers~\cite{smith94,chang1999,dang2006} were used.
The previously generated \cite{botan15} Lipid14 parameters in Gromacs format were downloaded from Ref.~\citenum{lipid14files}. 
The Lipid17 parameters were obtained from AmberTools18 \cite{amber18} 
and converted to Gromacs format using acpype \cite{acpype}.  
The ion model by Dang and coworkers~\cite{smith94,chang1999,dang2006} was used with Amber lipids because
the default Amber ion parameters \cite{aqvist90} led to the artificial clustering of ions in solution \cite{NMRlipidsIV}.
In the ECC-lipid simulations,
the ECC-POPC parameters~\cite{melcr18} (available from Ref. \citenum{ECC-POPC_nacl_cacl2_files}), 
the ECC-POPS parameteres derived in this work (section \ref{section:ecc}), 
the SPC/E~\cite{Berendsen1987} water model, and ECC-ions \cite{martinek17, kohagen16, Pluharova2014} were used.
The SPC/E water model was selected because its lower dielectric constant is consistent with the
ECC concept \cite{leontyev11,leontyev14}.
\begin{table}[tbp]
  \caption{Simulation parameters}
  \label{tbl:mdpar}
  \begin{tabular}{ll}
    simulation property & parameter   \\
    \hline
    time-step           & 2~fs         \\
    equilibration time  & 50~ns  \\
    total simulation time     & 1~$\mu$s  \\
    temperature         & 298~K       \\
    thermostat          & v-rescale  \cite{bussi07}   \\
    barostat            & Parrinello-Rahman, semi-isotropic \cite{parrinello81} \\
    long-range electrostatics & PME  \cite{darden93}  \\
    cut-off scheme      & Verlet \cite{Pall13}      \\
    Coulomb and VdW cut-off & 1.0~nm \\
    constraints         & LINCS, only hydrogen atoms \cite{hess97} \\
    constraints for water & SETTLE  \cite{miyamoto92} \\
    \hline
  \end{tabular}
\end{table}

>>>>

Here, we apply the ECC to the Amber based lipid17 parameters \cite{lipid17-future} of POPS lipid with a monovalent negative charge.
Because POPS carries a physical total charge as ions in water, we apply the theoretically derived scaling factor for
ions $f_q = 0.75$ \cite{leontyev09} to the partial charges of POPS. The lipids with a total charge of -0.75 also neutralize
the counterion charges of +0.75 in simulations with ECC-ions \cite{kohagen16}.
Following our previous work for POPC, we use the scaling factor of $f_\sigma = 0.89$ for the Lennard-Jones~$\sigma$ parameters and
scale the parameters of atoms only in the headgroup, glycerol backbone, and carbonyl regions \cite{melcr18}.
Further optimization of parameters was not done in this work.
\todo{Add here a reference to the parameters.}
% we used exactly the pre-determined scaling factor 
%to represent the effects of electronic polarization
%yielding a total charge of $-0.75$ in the ECC formalism. \cite{martinek17, leontyev09, melcr18}
%polar parts of the phospholipid,
%i.e., charges on all atoms except on alkyl tails, 
%which do not encounter direct contacts with ions.

@@

In the reference simulations with the standard Amber force field,
the Lipid14 parameters~\cite{dickson14} for POPC, the Lipid17 parameters for POPS \cite{lipid17-future},
the TIP3P water model~\cite{jorgensen83}, and ion models by Dang and coworkers~\cite{smith94,chang1999,dang2006} were used.
The previously generated \cite{botan15} Lipid14 parameters for POPC in Gromacs format were downloaded from Ref.~\citenum{lipid14files}. 
The Lipid17 parameters for POPS were obtained from AmberTools18 \cite{amber18} 
and converted to Gromacs format using acpype \cite{acpype}.  
The ion model by Dang and coworkers~\cite{smith94,chang1999,dang2006} was used with Amber lipids because
the default Amber ion parameters \cite{aqvist90} led to the artificial clustering of ions in solution \cite{NMRlipidsIV}.
In the ECC-lipid simulations,
the ECC-POPC parameters~\cite{melcr18} (available from Ref. \citenum{ECC-POPC_nacl_cacl2_files}), 
the ECC-POPS parameteres derived in this work (see above), 
the SPC/E~\cite{Berendsen1987} water model, and ECC-ions \cite{martinek17, kohagen16, Pluharova2014} were used.
The SPC/E water model was selected because its lower dielectric constant is consistent with the
ECC concept \cite{leontyev11,leontyev14}.
\begin{table}[tbp]
  \caption{Simulation parameters}
  \label{tbl:mdpar}
  \begin{tabular}{ll}
    simulation property & parameter   \\
    \hline
    time-step           & 2~fs         \\
    equilibration time  & 50~ns  \\
    total simulation time     & 1~$\mu$s  \\
    temperature         & 298~K       \\
    thermostat          & v-rescale  \cite{bussi07}   \\
    barostat            & Parrinello-Rahman, semi-isotropic \cite{parrinello81} \\
    long-range electrostatics & PME  \cite{darden93}  \\
    cut-off scheme      & Verlet \cite{Pall13}      \\
    Coulomb and VdW cut-off & 1.0~nm \\
    constraints         & LINCS, only hydrogen atoms \cite{hess97} \\
    constraints for water & SETTLE  \cite{miyamoto92} \\
    \hline
  \end{tabular}
\end{table}
